{\bf \Large THESISSSS}

### 2023-05-23 draft.tex
wrote conclusion

In this

 I show that not only this model is able to capture context succesfully, but also information it provides has meaningful contribution to traditional choice model. One can utilize this information to partly address the drawbacks of such models like logit and probit. However, the nature of computational models only allows them to account for the context as aggregate. To address this drawback in

 This research introduced a flexible framework for accounting for context effects across various settings and with large and complex product menus. The methodology proved to adaptable to inconsistent menu sizes and is not confined to a single empirical application. Its potential extends to large-scale data from e-commerce websites and offline sources, enabling context effect research without costly experimental interventions. Consequently, this method can aid in designing optimal offers and enhancing recommender systems, especially for online outlets presenting large arrays of options.

 The approach remains robust to selection criteria and contextualization method used, highlighting the efficiency and speed of implementation which is of essence in online environments. It further underscores the critical role of choice set context effects in influencing user decisions and demonstrates the potential of integrating these effects into recommender system design.

>>>>

The first part of the results produced in these four studies together provide significant insights into the influence of context effects into decision making and their application to recommender systems design. The second part of the results outlines the importance of user participation and their significance in recommender systems success.

The first study demonstrated the successful application of computational models to field data, showcasing the capacity of such models to extract convoluted patterns from complex real-world choice environments, thus potentially enhancing our understanding of context effects. In the second study, the calculations underscored the prominence of multidimensional context effects, highlighting the potential for improved understanding of decision making influenced by the varying contexts and interplay between them. The third study presented an effective solution to the continuous cold-start problem in RS design using context driven , two-step choice modeling approach, magnifying the potential of these effects in a path forward for recommender systems struggling with these issues. Lastly, the fourth study identified nuanced relationships between user control and recommender systems acceptance, suggesting that the introduction of control mechanisms can lead to a higher user acceptance and engagement with such systems.

The implications of these studies collectively suggest a innovative vision for the design and functioning of recommender systems. The successful application of computational model to field data in the first study showcases the potential of those models as a valuable tool for organizations seeking to gain insights into complex relationship among alternatives. It shows that not only this model is able to capture the context successfully, but also information it provides has meaningful contribution to widely used models.

The second study sheds light on the importance of considering multiple dimensions when analyzing context effects, suggesting their potential in building optimal sets in recommender systems. This research introduced a flexible framework for accounting for context effects across various settings and with large and complex product menus. The framework proved to be adaptable to inconsistent menu sizes and is not confined to a single empirical application. Its potential extends to large-scale data from e-commerce websites and offline sources, enabling context effect research without costly experimental interventions. Consequently, this method can aid in designing meaningful consideration sets and enhancing recommender systems, especially for online outlets presenting large arrays of options.

In the third study, the proposed solution to the continuous cold-start problem can substantially improve the performance of systems that tackled such challenges, streamlining the user decision-making process. The solution remains robust to selection criteria and contextualization method used, highlighting the efficiency and speed of implementation which is of essence in online environments. It further underscores the critical role of choice set context effects in influencing user decisions and demonstrates the potential of integrating these effects into recommender system design.

Lastly, the fourth study suggests that offering dynamic control mechanisms in line with a user's familiarity and requirements could lead to higher engagement and greater acceptance of recommender systems. These implications together pave the way for more sophisticated, user-centric recommender systems that balance complex relationships in multidimensional choice environments and ease-of-use, potentially revolutionizing the way users interact with such systems in an increasingly digital world.

The studies provided in this dissertation have several important limitations. First, the methodology proposed in the first study is able to account for context effects strictly arising from ordinal relationships. This leaves out the potential of the usage of cardinal measurements which were previously used. To address this one can potentially introduce another criterion to calculations, the magnitude of the relationship. This can be done for example, comparing alternatives not only based on "good or bad", but also "how much". Second, the two-stage modeling approach although proving itself useful, its direct implementation into modern systems is not straight forward. The predictive power of recommender systems have traditionally been (and still is) the most important metric. Applying such approach to any existing recommender system would not be feasible unless the amendments are made to make it predictive ability more salient. Thirdly, the user control mechanisms implemented in the fourth study were limited in numbers. This leaves out many other control mechanisms which use different interaction types to achieve similar goals. A possible way to address this limitation would be studying user control in even more complex experimental setting while ensuring the domain neutrality.
